Examining equity in accessibility to bike share: a balanced floating catchment area approach

### 2021-10-14 Bike-share-spatial-equity/Bike-share-spatial-equity.tex
Revisions after reviewer comments R2

This paper is an example of open and reproducible research that uses
only open software for transportation and statistical analysis (Bivand,
2020; Lovelace, 2021). All data were obtained from publicly available
sources and organized in the form of a data package. Following best
practices in spatial data science (Brunsdon and Comber, 2020), an open
data product (Arribas/Bel et al., 2021) along with the code needed to
reproduce, modify or extend the analysis are available for
download.\footnote{https://github.com/paezha/Accessibility-Sobi-Hamilton}

@@

\hypertarget{average-threshold}{%
\subsubsection{5.1.2. Average Threshold}\label{average-threshold}}

@@

\hypertarget{maximum-threshold}{%
\subsubsection{5.1.3. Maximum Threshold}\label{maximum-threshold}}

@@

\leavevmode\hypertarget{ref-arribas2021open}{}%
Arribas/Bel, D., Green, M., Rowe, F., Singleton, A., 2021. Open data
products: A framework for creating valuable analysis-ready data. Journal
of Geographical Systems.
doi:\href{https://doi.org/10.1007/s10109-021-00361-7}{10.1007/s10109-021-00361-7}

>>>>

This paper is an example of open and reproducible research that uses
only open software for transportation and statistical analysis (Bivand,
2020; Lovelace, 2021). All data were obtained from publicly available
sources and organized in the form of a data package. Following best
practices in spatial data science (Brunsdon and Comber, 2020), an open
data product (Arribas-Bel et al., 2021) along with the code needed to
reproduce, modify or extend the analysis are available for
download.\footnote{https://github.com/paezha/Accessibility-Sobi-Hamilton}

@@

\hypertarget{medium-threshold}{%
\subsubsection{5.1.2. Medium Threshold}\label{medium-threshold}}

@@

\hypertarget{high-threshold}{%
\subsubsection{5.1.3. High Threshold}\label{high-threshold}}

@@

\leavevmode\hypertarget{ref-arribas2021open}{}%
Arribas-Bel, D., Green, M., Rowe, F., Singleton, A., 2021. Open data
products: A framework for creating valuable analysis ready data. Journal
of Geographical Systems.
doi:\href{https://doi.org/10.1007/s10109-021-00363-5}{10.1007/s10109-021-00363-5}
